\chapter{Acknowledgements}

This work is the results of years of rumination about buildings and what might make the biggest impact in understanding the way they are operated. This end goal is important, but it is not as meaningful as the process and the people who provided support, insight and love to help achieve it. 

The Architecture and Building Systems Group in Zurich provided me with an environment and camaraderie to make this work possible. Prof. Arno Schlueter was an outstanding leader who organized the smartest group of people I've ever worked with. Daren needs to be thanked for cheese, hugs, jokes, and runs through the woods. Valerie was always there to answer questions and help navigate all the administrative challenges. PJ, Bratislav, Geroid, Anya, Christian, and Michele provided guidance and stimulating conversations. The Singapore FCL, 3for2 and UWC teams, including Adam, Yuzhen, Marcel, Forrest, Simon and Kenny and others made it possible and enjoyable to complete this work in Singapore. 

I'd like to thank all the external collaborators who made the data collection and analysis process possible. The facilities management teams from the various case study campuses provided the data, insight, and effort that made this work possible. Greg Fanslow and the VEIC team were invaluable in the analysis of AMI data.

My friends in Singapore, Zurich and the USA are too numerous to specifically mention, but their friendship is what made the process possible through both the good and difficult times. 

My family is the foundation for my work. Mel and Jerry provided unwavering support and love, despite my insistence to live my dreams abroad. Rick, Cassie, Kim, and Jarred were all there as supports and huge role models for myself and their beautiful families. Ethan, Leah, Derick, Aaron, Issac, Lily, Autumn, and Emily are my inspiration. 
