\section{Characterization of General Industry Membership and Energy-Savings Measure Implementation Success}
\label{sec:scalability}

In the previous sections, the process of temporal feature extraction and interpretation is implemented on a test set of 507 buildings. One of the key pieces of feedback from the case study interviews was that conventional analysis and meta-data collection for a set of buildings at this level is reasonable if the resources are allocated. This assumption quickly becomes untenable when discussing the analysis of the millions of buildings with smart meter data. These data are also known as Advanced Metering Infrastucture (AMI) data.  In this section, execution of a subset of the temporal feature extraction process is applied to a data set of close to 10,000 buildings that have been aggregated by a third-party organization on behalf of electrical utilities. The utilization goal of these data is to supplement a process of targeting buildings for energy savings implementation measures. Utilization of temporal features is discussed in the context of assisting to label the approximate building use type and predicting measure success implementation through a combination of smart meter data and past project experience meta-data. These objectives are common in situations with large amounts of AMI data as often the only meta-data available for these buildings is related to the location and demographic characteristics of a building. 

% Out of the 40,000 buildings, only around 9,600 have a significant amount of known meta-data. This situation leaves over 30,400 accounts as essentially unlabeled and thus, very difficult to use in analysis.

% The other challenge is that VEIC has a rich repository of data from thousands of past implementation projects in a system known as KITT. There is a huge potential in using information from past projects to predict the success of future implementations. There are 3,000 AMI accounts with data overlapping with the KITT database between January 2013 and June 2015. Manual analysis of this data overlap is time consuming to predict measure success is not trivial.
